### 2015-08-10 Paper1rev3/paper1rev2.tex
will this work?

Since trajectories were not controlled experimentally, our tests rely heavily on the assumption that disturbed intentions initially mirror undisturbed intentions. Therefore, it is not completely certain that subjects intended to move along a straight line to the target. However, this study examined straight line motions because it is well understood that people tend to repetitively attempt to reach in a straight line towards a target \cite{hodgson2000model}. Also, even when subjects are persistently perturbed by a force field, they recover their motions to a straight line with repetitive experience \cite{shadmehr1994adaptive}. Nevertheless, it may be better to employ tasks with a more specific trajectory in order to validate the intended path. Unfortunately, even such an intended trajectory may not be strictly invariant during external disturbance because some displacements may cause intent to be recalculated by the nervous system.

@@

The simple linear scaling of Burdet et al.'s stiffness model \cite{burdet2006stability} facilitated hypothesis testing, but was inherently limiting. More accurate approaches would provide us with many free parameters through which to determine the outcome of the eventual extraction and obtain a spurious favorable result. Like others who have examined large force disturbances, we find lower stiffnesses (our $c$ parameter) than might be expected \cite{crevecoeur2014beyond} (Table in S1 Table). This may be due to differences in tasks \cite{gomi1998task} and/or the dependency of muscle impedance on perturbation size \cite{van2010vivo}. Our results also point to the possibility of the impedance changing during motion, perhaps as a function of time.

>>>>

@@

The simple linear scaling of Burdet et al.'s stiffness model \cite{burdet2006stability} facilitated hypothesis testing, but was inherently limiting. More accurate approaches would provide us with many free parameters through which to determine the outcome of the eventual extraction and obtain a spurious favorable result. Our results point to the possibility of the impedance changing during motion, perhaps as a function of time.
